---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# `{wrappingtransformers}`

<!-- badges: start -->
<!-- badges: end -->

`{wrappingtransformers}` provides acess to some functions of some pretrained NLP models shared on Hugging Face's model community platform through R that you'd normally access using Python.

- Currently implemented:
  - [`flair/ner-german-large`](https://huggingface.co/flair/ner-german-large)
    - sequence tagger
- Planned:
  - [`flair/ner-german`](https://huggingface.co/flair/ner-german)
    - sequence tagger
  - [`deepset/bert-base-german-cased-hatespeech-GermEval18Coarse`](https://huggingface.co/deepset/bert-base-german-cased-hatespeech-GermEval18Coarse)
    - text classification

## Basic Installation

Because `{wrappingtransformers}` has Python dependencies, the setup is a bit more complicated than usual — you'll have to run some extra commands before you can use it.

If you just want to use transformers from within R, run the following commands in R. This will create a local Python installation that will only be used by R and install the needed Python package for you.

```{r}
install.packages("reticulate")
reticulate::install_miniconda(update = TRUE) # Install Python
reticulate::py_install('transformers') # Install the Python transformers package
remotes::install_github("balthasars/wrappingtransformers") # Install this package
```

__After running these commands restart R.__

## Advanced Setup — Select the Python version to be used 

Discover what version of Python will be used unless you set it manually as suggested below. [transformers is tested with Python 3.6](https://github.com/huggingface/transformers).

```{r}
reticulate::py_discover_config()
```

If you're happy with what this indicates, you may skip over the following steps.

If not, set the environmental varible `RETICULATE_PYTHON` to the desired Python version path interactively with `usethis::edit_r_environ()` or using `Sys.setenv()`:

```{r}
Sys.setenv(RETICULATE_PYTHON = "/usr/local/bin/python3.9")
```


Alternatively you can select the Python environment using the reticulate package:

```{r}
reticulate::use_python(python = "/usr/local/bin/python3.9")
```

### Select Environment

Use `create_wrappingtransformers_venv()` to create a new environment solely for the purpose of using this package. 

This will install all required Python libraries using the version of python indicated in the environment variable `RETICULATE_PYTHON` if you don't indicate it in argument `python_path`. 

```{r}
create_wrappingtransformers_venv(python_path = NULL)
```

If you already have a Python environment with transformers installed, name it in the `virtualenv` argument. 
This will set it up for the rest of this R session.

```{r}
reticulate::use_virtualenv(virtualenv = "myenv")
```

or use Conda:

```{r}
reticulate::use_condaenv(condaenv = "myenv")
```

## Using the models

### `flair/german-ner-large`

Here's how to use the NER tagger:

```{r}
wt_load_model(model_name = "ner_german_large")
sentence_example <- "Santesuisse und Curaviva fordern eine Umverteilung"
wt_predict_labels_ner_german_large(sentence = sentence_example)
```

